### 2021-01-18 README.Rmd
migrate to github actions for CI

[![Travis Build Status](https://travis-ci.org/rudeboybert/forestecology.svg?branch=master)](https://travis-ci.org/rudeboybert/forestecology)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/forestecology)](https://cran.r-project.org/package=forestecology)

>>>>

[![Build Status](https://github.com/rudeboybert/forestecology/workflows/R-CMD-check/badge.svg)](https://github.com/rudeboybert/forestecology/actions)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/forestecology)](https://cran.r-project.org/package=forestecology)
